### 2021-04-27 input/proposal.tex
spacing

Algorithm~\ref{algo:edges} extends the instructions of \NAME that
enable dynamic consistent partitioning in dynamic networks where
\processes can join or leave the system without notification. We
consider that removing a \process is equivalent to removing all its
edges, and adding a \process is equivalent to add as many edges as
necessary.

Adding an edge between two \processes may only improve the shortest
path of one of these \processes. Therefore, it triggers a competition
between the two \processes only. If one or the other \process
improves, the propagation of $\alpha$ messages operates normally.

\noindent Removing an edge between two \processes may invalidate the
shortest path of one of involved \processes plus downstream
\processes. As a side effect, removing an edge may also impair the
propagation of a partition delete. To implement this behavior, \NAME
uses its implementation of $\delta?$ messages. This prove costly but
enables \NAME even in dynamic networks subject to physical
partitioning.

>>>>

Algorithm~\ref{algo:edges} extends \NAME to enable dynamic consistent
partitioning in dynamic networks where \processes can join or leave
the system without notification. We consider that removing a \process
is equivalent to removing all its edges, and adding a \process is
equivalent to add as many edges as necessary.

Adding an edge between two \processes may only improve the shortest
path of one of these \processes. Therefore, it triggers a competition
between the two \processes only. If one or the other \process
improves, the propagation of $\alpha$ messages operates normally.
Removing an edge between two \processes may invalidate the
shortest path of one of involved \processes plus downstream
\processes. As a side effect, removing an edge may also impair the
propagation of a partition delete. To implement this behavior, \NAME
uses its implementation of $\delta?$ messages. This prove costly but
enables \NAME even in dynamic networks subject to physical
partitioning.
